The ChEMBL database as Linked Open Data

### 2012-08-15 article.tex
Fixed the link to Bio2RDF EC numbers: that is not an equivalence relationship, but a classification

\begin{small}
\begin{verbatim}
target:t101191
 chembl:hasTaxonomy <http://bio2rdf.org/taxonomy:9606> ;
 owl:sameAs <http://bio2rdf.org/ec:2.7.11.1> ;
 owl:sameAs <http://bio2rdf.org/uniprot:Q8IYT8> .
\end{verbatim}
\end{small}

>>>>

\begin{small}
\begin{verbatim}
target:t101191
 chembl:hasTaxonomy <http://bio2rdf.org/taxonomy:9606> ;
 rdfs:subClassOf <http://bio2rdf.org/ec:2.7.11.1> ;
 owl:sameAs <http://bio2rdf.org/uniprot:Q8IYT8> .
\end{verbatim}
\end{small}
